---
title: "MAT 124 - MRSA Project: Midterm 2"
author: "Ryan Campbell, Riley Adams, Aditya Kurkut"
date: "5/14/2022"
output:
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE,echo=FALSE,message=FALSE,warning=FALSE}
# setwd("I:/My Drive/Spring 2022/MAT 124/midterm2/MAT-124-MRSA-Project")

library("dplyr")
knitr::opts_chunk$set(echo = TRUE)
## General Notes
  # Installed Library BiocManager (> install.packages("BiocManager")
  # Installed package msa (> BiocManager::install("msa"))
  # View documentation (> browseVignettes("msa")). Click on pdf, source, or R code.


## Other packages we may want to consider:
  # For sequences: ClustalW, Clustal omega (recommended) and MUSCLE within R.
  # For phylogenetic trees: MEGA (external resource) or Phylogram within R.
  # For reticular evolution: TDA (topological data analysis) within R. Dr. Arsuaga mentions RDP4 (Not sure what language/software)
  # For BLAST: https://blast.ncbi.nlm.nih.gov/Blast.cgi?PROGRAM=blastn&PAGE_TYPE=BlastSearch&BLAST_SPEC=&LINK_LOC=blasttab&LAST_PAGE=blastp
```

```{r, message=FALSE,warning=FALSE,echo=FALSE}
# read in the data
library(readr)
pnas_1702472114_sd04 <- read_delim("pnas.1702472114.sd04.txt", 
    delim = ">", escape_double = FALSE, trim_ws = TRUE)
View(pnas_1702472114_sd04)

#~~~~ clean the data ~~~~~~~~~

# create/names for dataframe mrsa
mrsa <- data.frame(cbind(pnas_1702472114_sd04[2],pnas_1702472114_sd04[1]))
mrsa[1,1] <- "USA_2001_2"
colnames(mrsa) <- c("strain","sequences")

#align sequences with their strains
for (i in 2:length(mrsa$sequences)) {
  if (i %% 2 == 0){
    mrsa$sequences[i] <- mrsa$sequences[i+1]
  }
}

# remove extra copies of sequences corresponding to NA strains
# (need to remove odd rows from data frame after row 2)
mrsa <- mrsa %>% filter(mrsa$strain != "NA")
```

```{r, message=FALSE,warning=FALSE,echo=FALSE}
library("ape")
library("Biostrings")
library("ggplot2")
library("ggtree")
# Need a Newick or Nexus tree format. "It also reads outputs from a range of tree-building software such as BEAST, EPA, HYPHY, PAML, PHYLDOG, pplacer, r8s, RAxML and RevBayes."
# nwk <- system.file("mrsa", "sample.nwk", package="ggtree")
# tree <- read.tree(nwk)
# tree
```


# Abstract

In this study we examine the evolution of community-acquired methicillin-resistant Staphylococcus *aureus* (CA-MRSA), an antibiotic resistant form of the common bacteria Staphylococcus aureus. Of particular interest, is the lineage of a hypervirulent, pandemic clone of the bacteria which has been spreading globally. First discovered in the United States in the early 2000's, as a new kind of MRSA which was no longer unique to healthcare environments started gaining prominence, the CA-MRSA clone was aptly named USA300. USA300 is of a certain type of S. *aureus* known as multilocus sequence type 8, henceforth referred to as ST-8. We examine the genetic similarity and evolution of 224 isolates of ST-8 type S. *aureus* in order to gain insight into the background and spread of USA300 and related CA-MRSA clones.

# Introduction

# Methods and Results

### Phylogenetic Tree Analysis

### Topological Data Analysis

# Discussion

# Author Contribution

# Resources




























