---
title: "MAT 124 - MRSA Project: Midterm 2"
author: "Ryan Campbell, Riley Adams, Aditya Kurkut"
date: "5/14/2022"
output:
  html_document: default
  pdf_document: default
---
```{r, echo=FALSE}
# paste your file path to the project here in the setwd() function as I have below
# you can copy/paste this code into your console and run it to easily set your
# working directory to the clone of the repository

# setwd("I:/My Drive/Spring 2022/MAT 124/midterm2/MAT-124-MRSA-Project")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# libraries
library("dplyr")
library(seqinr)
library(adegenet)
library(ape)
library(ggtree)
library(DECIPHER)
library(viridis)
library(ggplot2)
```

# Abstract

In this study we examine the evolution of community-acquired methicillin-resistant Staphylococcus *aureus* (CA-MRSA), an antibiotic resistant form of the common bacteria Staphylococcus aureus. Of particular interest, is the lineage of a hypervirulent, pandemic clone of the bacteria which has been spreading globally. First discovered in the United States in the early 2000's, as a new kind of MRSA which was no longer unique to healthcare environments started gaining prominence, the CA-MRSA clone was aptly named USA300. USA300 is of a certain type of S. *aureus* known as multilocus sequence type 8, henceforth referred to as ST-8. We examine the genetic similarity and evolution of 224 isolates of ST-8 type S. *aureus* in order to gain insight into the background and spread of USA300 and related CA-MRSA clones.

# Introduction

# Methods and Results

## Phylogenetic Tree Analysis

## Topological Data Analysis

# Discussion

# Author Contribution

# References




























